---
title: "decision accuracy simulation"
author: "Iris Yocarini"
date: "22 May 2016"
output: html_document
---
#Simulation Decision Accuracy
### Import data
In a different project, this data was simulated. Under 144 different conditions (full factorial model), 500 datasets were simulated with each simulation containing simulated grades from 2000 students. 

```{r}
datasim <- read.csv("~/Rworkspace/simdata/datasetsimulatiespaper", sep="")
str(datasim, list.len=ncol(datasim))
```

### Descriptives

#### Manipulated variables
The 144 conditions were created using a full factorial model of four variables that were manipulated:

* The number of tests were manipulated at `r length(unique(datasim$n))` levels: n = `r unique(datasim$n)`
* The correlation between the tests was manipulated at `r length(unique(datasim$cor))` levels: cor = `r unique(datasim$cor)`
* The average reliability of the tests was manipulated at `r length(unique(datasim$R))` levels: R = `r unique(datasim$R)`
* The number of tests allowed to be retaken were manipulated at `r length(unique(datasim$z))` levels: cor = `r unique(datasim$z)`

#### Decision rules
In total 15 decision rules were applied to each simulated dataset. In each of these rules different GPA and minimum grades were required. In order to pass the year, students needed to score above a 5.5, 6, or 6.5 and have a minimum grade of 1.0, 3.0, 4.0, or 5.0 on each individual test.

`r rules <- matrix(c(5.5,1.0,3.0,4.0,5.0,6.0,1.0,3.0,4.0,5.0,6.5,1.0, 3.0,4.0,5.0,5.5,5.5,5.5,5.5,5.5,6.0,6.0,6.0,6.0,6.0,6.5,6.5,6.5,6.5,6.5),15,2)`
`r rownames(rules) <- c("decision 1",
                     "decision 2",
                     "decision 3",
                     "decision 4",
                     "decision 5",
                     "decision 6",
                     "decision 7",
                     "decision 8",
                     "decision 9",
                     "decision 10",
                     "decision 11",
                     "decision 12",
                     "decision 13",
                     "decision 14",
                     "decision 15")`
`r colnames(rules) <- c("Minimum grade", "GPA")`
```{r}
print(rules)
```

### Results
## Total proportion of misclassifications 
```{r}
library(ggplot2)
g <- ggplot(data = datasim, aes(x=R, y=rule1total, group = n)) 
g + geom_boxplot()
g <- ggplot(data = datasim, aes(x=R, y=rule2total, group = n)) 
g + geom_boxplot()
```